Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-27 doc/main_jfm.tex
added in-line data to 4.2

\subsection{Model Parameters}
In the present manuscript, the particles are disks with centre $\aa_i$, and director $\dd_i$.  
The boundary conditions \eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos \theta_i)$ where $\theta_i$ is the angle between 
$\xx - \aa_i$ and $\dd_i$.  The particle diameters are $l_0 = 2.5$ nm representing the characteristic thickness of monolayer. 
The other physical parameters are 
\begin{equation}
\label{eq:parameters}
\rho = 4 l_0,\quad \rho_0 = l_0,\quad \gamma = \text{4 pN nm}^{-1},\quad \mu = \text{1 cP}.
\end{equation}
We nondimensionalize the problem through the change of variables 
\begin{equation}
\label{eq:nondimensionalize}
t \mapsto t \text{ ns}, \quad
\xx \mapsto \xx \text{ nm}, \quad 
\xx \mapsto \xx \text{ nm}, \quad 
\uu \mapsto \uu \text{ nm ns}^{-1}, \quad 
  p \mapsto p \text{ pN nm}^2.
\end{equation}
Here $\text{1 cP} = \text{1 pN ns nm}^{-2}$ is for the viscosity of water at room temperature.  
For the rest of the manuscript, the time axes are for ns; the pressure $p$ and stress $\sigma$, $\mathbf{T}^{\mathrm{hydro}}$
are for pN nm$^{-2}$.

@@

The particles in our setup do not abut but rather have small gaps due to repulsive forces.
The gaps allow for some fluid flux across the JP bilayer.  Aqueous flux is quantified by a permeability constant $P$ in the equation
\begin{equation}
\label{eq:perm}
\frac{dA}{dt} = -P  L \Delta p.
\end{equation}
Combining \eqref{eq:stretch}, \eqref{eq:LaplacePressure}, and \eqref{eq:perm}, we can solve the for length $L$ 
\begin{equation}
L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t
\end{equation}
and compare with our data.

>>>>

\subsection{Model Parameters}
In the present manuscript, the particles are disks with centre $\aa_i$, and director $\dd_i$.  
The boundary conditions \eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos \theta_i)$ where $\theta_i$ is the angle between 
$\xx - \aa_i$ and $\dd_i$.  The particle diameters are $l_0 = 2.5$ nm representing the characteristic thickness of monolayer. 
The other physical parameters are 
\begin{equation}
\label{eq:parameters}
\rho = 4 l_0,\quad \rho_0 = l_0,\quad \gamma = \text{4 pN nm}^{-1},\quad \mu = \text{1 cP}.
\end{equation}
We nondimensionalize the problem through the change of variables 
\begin{equation}
\label{eq:nondimensionalize}
t \mapsto t \text{ ns}, \quad
\xx \mapsto \xx \text{ nm}, \quad 
\xx \mapsto \xx \text{ nm}, \quad 
\uu \mapsto \uu \text{ nm ns}^{-1}, \quad 
  p \mapsto p \text{ pN nm}^{-2}.
\end{equation}
Here $\text{1 cP} = \text{1 pN ns nm}^{-2}$ is for the viscosity of water at room temperature.  
For the rest of the manuscript, the time axes are for ns; the pressure $p$ and stress $\sigma$, $\mathbf{T}^{\mathrm{hydro}}$
are for pN nm$^{-2}$.

\begin{figure}
\centering
\includegraphics[width=0.32\textwidth]{PermPanelA.pdf}
\includegraphics[width=0.32\textwidth]{PermPanelB.pdf}
\includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
  \caption{}
    \label{figure:permeability}
\end{figure}

@@

The particles in our setup do not abut but rather have small gaps due to repulsive forces.
The gaps allow for some fluid flux across the JP bilayer.  Aqueous flux is quantified by a permeability constant $P$ in the equation
\begin{equation}
\label{eq:perm}
\frac{dA}{dt} = -P  L \Delta p.
\end{equation}
Combining \eqref{eq:stretch}, \eqref{eq:LaplacePressure}, and \eqref{eq:perm}, we can solve the for length $L$ 
\begin{equation}
\label{eq:perm_solution}
L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t
\end{equation}
and compare with our data.

Data obtained for the above model.
Case 1. 58 particles with diameter 2.5 nm and $L_0 = 107$ nm. The calculated stretching modulus was $K_A = 109$ pN nm$^{-1}$ which gives 26.5 kT nm$^{-2}$.
This value is in good agreement with the 60 kT nm$^{-2}$ from experimental measurements.  The calculated permeability was 
$0.0296$ nm$^3$ ns$^{-1}$ pN$^{-1}$ = 
$0.0296$ $\mu$m s$^{-1}$ Pa$^{-1}$. (double check value; too large)
Case 2. 117 particles with diameter 1.25 nm and $L_0 = 141$ nm. This data set gave  $K_A = 62$ pN nm$^{-1}$ which gives 15 kT nm$^{-2}$ which is small.
For permeability we get 0.0566 $\mu$m s$^{-1}$ Pa$^{-1}$.

The dashed lines in panel (a) are the graphs of \eqref{eq:perm_solution} for the 58 and 117 particle number cases, respectively. 
Panels (b) and (c) show the select data points with plusses for 58 particles and times for 117 particles.  The solid lines are linear fits.
The linear fits in panel (b) shows that $R\Delta P$ is proportional to relative stretching $L/L_0 - 1$. The proportionality constant is $K_A.$
The linear fits in panel (c) shows that $L\Delta P$ is proportional to flux $\frac{dA}{dt}$.  The proportionality constant is the permeability coefficient $P.$
